### 2015-06-07 LOI/inc2.tex
Quick pass.

\underline{\textbf{Objectives:}} Exascale scientific discovery will be
severely bottlenecked without sufficient new research into managing and
storing the large amounts of data that will be produced during the
simulation, and analyzed for months afterwards.  Our goal in this project is
to address the associated I/O and storage challenges in the context of
current ancd emerging storage landscapes, and expedite insights into mission
critical scientific processes. To that end, we will build on the
capabilities offered by ADIOS and DataSpaces that provide I/O abstractions
and services, the Sirocco peer-to-peer file system under development at
Sandia and the object storage and annotation expertise of UC Santa Cruz, to
explore application and multi-tier storage aware data management
solutions. Our solutions will provide novel functionalities and APIs for
% It will center upon a multi-tier storage-aware approach and incorporate new
% functionalities, extended object metadata and APIs for 
%
1) specifying, at the application level, data annotations that enable the
qualification of the relative importance and utility of data objects, and
enable them to be mapped at runtime to appropriate storage capabilities
across the storage hierarchy;
%
2) specifying selectable performance/quality/cost tradeoffs from both the
application and system perspectives; and
%
3) evaluating these tradeoffs at runtime during data placement and movement,
and executing the resultant policies in an autonomic system using models,
heuristics and continous learning,
%
4) Leveraging techniques such as application-aware data compression (both
lossy with specified error bounds and lossless), re-computation at the
requisite level of accuracy, and I/O prioritization to enforce these
policies.
%  2) a selectable performance/quality tradeoff when reading data, and
  %  the ability to recompute data if needed, and
  %  3) incorporate reader prioritization for data annotation, placement, and data
  %  quality when writing data.  
A key challenge in this project is defining and maintaining the metadata
connecting different object quality and utility levels, and using this metadata 
to most appropriately manage the placement and access of data object based on 
user/application intent/contraints and storage system state.
% to best enabling the user with the best possible outcomes 
% given the user intent and the storage system state. 
The new user APIs required to interact with this rich metadata system will
drive effective use of the entire middleware and storage stack.  The project
is comprised of a team with strong expertise in I/O middleware (ORNL,
Rutgers), file system (SNL, UCSC) and storage (UCSC), and connect and
coordinate these key storage components in a seamless fashion.

@@

\ALT{Our approach can be most easily understood by considering a traditional
  supermarket logistics problem. Given a limited amount of shelf space,
  fluctuating user demands and priorities, and the need to optimize profit at
  a market wide level instead of per product, the logistical problem combines
  predictions about the variants and the indicated constraints to find a
  solution. Self space is itself not a homogenous, with different locations
  providing greater rewards to the placed items. Furthermore, haphazard
  organization of items produces suboptimal results because it would ignore
  locality in purchasing. Backroom and warehouses represent tiers of storage
  where objects can be stored in bulk, but have a substantial overhead (and
  thus lower utility) in access. Similar to this scenario, the data management
  problem is a complex logistics problem. Shelf space is analagous to high
  performance/lower capacity storage. Locality is an important consideration,
  not just for single data objects but also through the identification of
  domain meaningful relationships between objects. The tiers of the storage
  hierarchy provide lower cost for data storage, but also increase the
  overhead for access.}

Our approach can most easily be understood by considering a road navigation
program. Similar to the navigation program, we will offer a coarse grained,
fast overview of a data set with progressively more detail in areas of
interest such as those contain features, and less detail in areas
without. These progressively more detailed data views require more storage
space and time to retrieve. By incorporating middleware informed of either
the criteria for identifying areas of interest or the intended use
locations, it will be able to selectively store data at different quality
levels, with bounded errors in the case of lossy compression, and allow a
user to select what data to retrieve by specifying both an acceptable
retrieval timeframe and error bound.
%  If the request
  %   cannot be fulfilled, the storage system can negotiate with the user providing
   %    information about the quality and timeframes available for a subsequent
    %     request.
     %%%%%%%%%%%%                 I am not sure if we should do this type of expert system in the project.
The user may also specify guidelines that are funneled through the I/O middleware and 
provide advice on how to react if the timeframe and error bound cannot be accepted.

>>>>

\underline{\textbf{Objectives:}} Exascale scientific discovery will be
severely bottlenecked without sufficient new research into managing and
storing the large amounts of data that will be produced during the
simulation, and analyzed for months afterwards.  Our goal in this project is
to address the associated I/O and storage challenges in the context of
current and emerging storage landscapes, and expedite insights into mission
critical scientific processes. To that end, we will build on the
capabilities offered by ADIOS and DataSpaces that provide I/O abstractions
and services, the Sirocco peer-to-peer file system under development at
Sandia and the object storage and annotation expertise of UC Santa Cruz, to
explore application and multi-tier storage aware data management
solutions. Our solutions will provide novel functionalities and APIs for
% It will center upon a multi-tier storage-aware approach and incorporate new
% functionalities, extended object metadata and APIs for 
%
1) specifying, at the application level, data annotations that enable the
qualification of the relative importance and utility of data objects, and
enable them to be mapped at runtime to appropriate storage capabilities
across the storage hierarchy;
%
2) specifying selectable performance/quality/cost tradeoffs from both the
application and system perspectives; and
%
3) evaluating these tradeoffs at runtime during data placement and movement,
and executing the resultant policies in an autonomic system using models,
heuristics and continuous learning,
%
4) leveraging techniques such as application-aware data compression (both
lossy with specified error bounds and lossless), re-computation at the
requisite level of accuracy, and I/O prioritization to enforce these
policies.
%  2) a selectable performance/quality tradeoff when reading data, and
  %  the ability to recompute data if needed, and
  %  3) incorporate reader prioritization for data annotation, placement, and data
  %  quality when writing data.  
A key challenge in this project is defining and maintaining the metadata
connecting different object quality and utility levels, and using this metadata 
to most appropriately manage the placement and access of data object based on 
user/application intent/constraints and storage system state.
% to best enabling the user with the best possible outcomes 
% given the user intent and the storage system state. 
The new user APIs required to interact with this rich metadata system will
drive effective use of the entire middleware and storage stack.  This project
brings together a unique team with strong expertise in I/O middleware (ORNL,
Rutgers), file system (SNL, UCSC) and storage (UCSC), and connect and
coordinate these key storage components in a seamless fashion.

@@

\ALT{Our approach can be most easily understood by considering a traditional
  supermarket logistics problem. Given a limited amount of shelf space,
  fluctuating user demands and priorities, and the need to optimize profit at
  a market wide level instead of per product, the logistical problem combines
  predictions about the variants and the indicated constraints to find a
  solution. Self space is itself not a homogenous, with different locations
  providing greater rewards to the placed items. Furthermore, haphazard
  organization of items produces suboptimal results because it would ignore
  locality in purchasing. Backroom and warehouses represent tiers of storage
  where objects can be stored in bulk, but have a substantial overhead (and
  thus lower utility) in access. Similar to this scenario, the data management
  problem is a complex logistics problem. Shelf space is analogous to high
  performance/lower capacity storage. Locality is an important consideration,
  not just for single data objects but also through the identification of
  domain meaningful relationships between objects. The tiers of the storage
  hierarchy provide lower cost for data storage, but also increase the
  overhead for access.}

\manish{I have tried to rework the text below, but I am still not comfortable with it. I have left the original text commented.

%Our approach can most easily be understood by considering a road navigation
%program. Similar to the navigation program, 
Incorporating awareness of the data content and user intent (to the extent possible) into
our decision making and data management process is integral to our approach. For example, 
we will offer a coarse grained, quick overview of a data set with progressively more detail in 
areas of interest such as those containing features, and less detail in areas
without. These progressively more detailed data views require more storage
space and time to retrieve. By defining mechanisms for applications to provide this 
knowledge and incorporating its awareness into our middleware 
%so that it is informed of either the criteria for identifying areas of interest or the intended use locations, 
it will be able to selectively store data at different quality levels, with bounded errors in the case of 
lossy compression, and allow a user to select what data to retrieve by specifying both an acceptable
retrieval timeframe and error bound.
%  If the request
  %   cannot be fulfilled, the storage system can negotiate with the user providing
   %    information about the quality and timeframes available for a subsequent
    %     request.
     %%%%%%%%%%%%                 I am not sure if we should do this type of expert system in the project.
The user may also specify guidelines that are funneled through the I/O middleware and 
provide advice on how to react if the timeframe and error bound cannot be accepted.
